---
title: "R Dokumentation"
author: "Daniel Smith"
date: "2024-06-21"
output: 
  html_document:
    toc: TRUE
    toc_depth: 3
    toc_float: 
      collapsed: FALSE
      smooth_scroll: TRUE
    number_sections: FALSE
    theme: united
    highlight: tango
    
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Einleitung

Ein paar hilfreiche Infos zur Erstellung des R Markdowns findet man unter 'R Markdown Doku'.
 

## Nützlich {.tabset .tabset-fade .tabset-pills}

### Literatur 

[Buch: Advanced R (second edition)](https://adv-r.hadley.nz/)

[Tidyverse Style](https://style.tidyverse.org/index.html)

[rlang](https://rlang.r-lib.org/) Provides a clean interface to low-level data structures and operations

[Shiny](https://shiny.posit.co/) Easy web apps for data science without the compromises

[R for Data Science](https://r4ds.hadley.nz/) Introduction to Tidyverse

```{r, child=c('child documents/RMarkdown.Rmd')}
```


### Online Communities

[RStudio Community](https://stackoverflow.com/)



# Part 1: Foundations {.tabset .tabset-fade .tabset-pills}

- Names and values
- Vectors  

```{r, child=c('child documents/Part 1/1_names and values.Rmd')}
```


```{r, child=c('child documents/Part 1/2_vectors.Rmd')}
```





