## Names and values {.tabset .tabset-fade .tabset-pills}

Outline: Understand the distinction between an object and its name  
Libraries of this chapter: [lobstr](https://lobstr.r-lib.org/)  

```{r, eval = FALSE}
?Memory
?gc
```

### Binding basics

```{r, eval=FALSE}
x <- 1:3
```
The phrase **'create an object named "x" containing the values 1, 2 and 3'** is a not fully accurate simplification.  

More accurate (two things):  
- creating an object, a vector of values 1, 2 and 3  
- bind that object to a name, **x**  

> You can think of a name as a reference to a value.


Intuition: A value does not have a name, but a name has a value.

Example: x and y reference to the same value

```{r, results = "hold"}
x <- 1:3
y <- x

lobstr::obj_addr(x)
lobstr::obj_addr(y)
```



**Reserved names:**  
*Non-syntactic* name: Complete list can be found via

```{r, eval = FALSE}
?Reserved
```

Examples are: 
```{r, eval = FALSE}
TRUE
FALSE
if
function
_abc
...

_abc <- 10
#> Fehler: unerwartetes Symbol in "_abc"

```


It is possible (but unwise) to overwrite these rules by **surrounding it with backticks**:  
```{r}
`_abc` <- 10
`_abc` 
```



### Copy-on-modify

```{r, results = "hold"}
x <- 1:3
y <- x

# Unmodified y
lobstr::obj_addr(x)
lobstr::obj_addr(y)

y[[3]] <- 4
x

# After modifying y
lobstr::obj_addr(x)
lobstr::obj_addr(y) # R created a new object

```
R created a new object **`r lobstr::obj_addr(y)`**, a copy of **`r lobstr::obj_addr(x)`**, and **y** reference to this new object. This behaviour is called **copy-on-modify**.

> R objects are immutable!

**Note:** There are a couple of important exeptions, which are discussed in this chapter!  
**Note:** The copy-on-modify behaviour generates different results by using RStudio interactively.
**Reason:** The environment pane must make a reference to each object in order to display information about it.


#### tracemem()

You can see when an objects getting copied by using `base::tracemen()`. The tracing is turned off by using `base::untracemem()`.

```{r, eval = FALSE}
x <- 1:3
cat(tracemem(x), "\n")
# <000002A9966E5170> 
y <- x
y[[3]] <- 4L
# tracemem[0x000002a9966e5170 -> 0x000002a994214808]: 
y[[3]] <- 5
# tracemem[0x000002a994214808 -> 0x000002a998590e18]: 
untracemem(y)
```



#### Function call

#### Lists




